Exp1 - Opt w_max and {A,phi)

### 2018-03-11 voltagebudget/analysis/paper_figures.Rmd
draft 1 for bound 1 fig complete

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
```

@@

```{r, message=FALSE}
# -
# Example voltage timecourses
results0 <- read_csv("vm_comp_timecourse.csv")

# -
# Sweep A
exp <- "72"
freqs <- c(8, 12, 20, 30)

# Load
results1 <- NULL
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

  df$freq <- rep(freq, nrow(df))
  results1 <- rbind(results1, df)
}

# Process
results1 %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> results1

@@

```{r, fig.width=1.5, fig.height=1.3}
results0 %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=vm)) +
  geom_ribbon(fill="blue", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  labs(x="", y="Vm") +
  theme_classic() -> p1

results0 %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
  # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
  # geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), color="grey", alpha=0.5) +
  # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
  labs(x="Times (s)", y="") +
  theme_classic() -> p2

results0 %>% 
  filter(t > 0.23652 - 8e-3, t < 0.23652 + 2e-3 + 0.03333333 + 8e-3) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
  # geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  # geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), fill="grey", alpha=0.01) +
  geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3),  fill="grey", alpha=0.01) +
  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
  labs(x="", y="") +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p3

@@

```{r, fig.width=1.3, fig.height=1.9}
results1 %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As*1e9, y=errors_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.6) + 
  labs(x="A (namp)", y="Error (ms)") +
  theme_classic() +
  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
  theme(legend.position="none") -> p1

results1 %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As*1e9, y=variances_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.6) + 
  labs(x="A (namp)", y="Variance (ms)") +
  lims(y=c(0, 12)) +
  theme_classic() +
  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
  theme(legend.position="right") -> p2

results1 %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.6) + 
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  scale_color_gradient2(low="grey", high="orange", midpoint = 1) +
  theme(legend.position="none") +
  labs(x="Error (ms)", y="Variance (ms)") -> p3

plot_grid <- rbind(c(1, 1, NA), c(2, 2, 2), c(3, 3, NA))
grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
```

@@

```{r, fig.width=1.25, fig.height=1.15}
results1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=As*1e9, y=1e3*V_osc)) +
  geom_point(size=0.1, alpha=0.01) + 
  labs(x="A (namp)", y="V_osc (mvolt)") +
  theme_classic() -> p1

plot_grid <- rbind(c(1))
grid.arrange(p1, layout_matrix=plot_grid)
```

>>>>

normalize <- function(x) {
    return ((x - min(x)) / (max(x) - min(x)))
}
data_summary <- function(x) {
   m <- mean(x)
   ymin <- m-mad(x)
   ymax <- m+mad(x)
   return(c(y=m,ymin=ymin,ymax=ymax))
}
mean_summary <- function(x) {
   m <- mean(x)
   return(c(y=m))
}
```

@@

```{r, message=FALSE}
# --------------------------------------------------------------------
# Example voltage timecourses
fig0 <- read_csv("vm_comp_timecourse.csv")

# --------------------------------------------------------------------
# Sweep A
exp <- "72"
freqs <- c(8, 12, 20, 30)

# Load
fig1 <- NULL
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=","))
  df %>%
    filter(n_spikes > 0) -> df

  df$freq <- rep(freq, nrow(df))
  fig1 <- rbind(fig1, df)
}

# Process
fig1 %>% 
  # Add delta_spikes
  mutate(delta_spikes = n_spikes - n_spikes_ref) %>% 
  # Re-norm V_osc
  mutate(V_osc = V_osc - V_osc_ref) -> fig1

# --------------------------------------------------------------------
# Summarize over As
fig1 %>% 
  group_by(As) %>% 
  summarise(
    V_osc = mean(V_osc), 
    V_comp = mean(V_comp), 
    errors = mean(errors), 
    variances = mean(variances)) -> fig2

@@

```{r, fig.width=1.5, fig.height=1.3}
fig0 %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=vm)) +
  geom_ribbon(fill="blue", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  labs(x="", y="Vm") +
  theme_classic() -> p1

fig0 %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
  # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
  # geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), color="grey", alpha=0.5) +
  # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
  labs(x="Times (s)", y="") +
  theme_classic() -> p2

fig0 %>% 
  filter(t > 0.23652 - 8e-3, t < 0.23652 + 2e-3 + 0.03333333 + 8e-3) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
  # geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  # geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), fill="grey", alpha=0.01) +
  geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3),  fill="grey", alpha=0.01) +
  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
  labs(x="", y="") +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p3

@@

```{r, fig.width=1.5, fig.height=2.0}
fig1 %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As*1e9, y=errors_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.6) + 
  labs(x="A (namp)", y="Error (ms)") +
  theme_classic() +
  scale_color_gradient(low="grey", high="black") +
  theme(legend.position="none") -> p1

fig1 %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As*1e9, y=variances_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.6) + 
  labs(x="A (namp)", y="Variance (ms)") +
  lims(y=c(0, 12)) +
  theme_classic() +
  scale_color_gradient(low="grey", high="black", name="Freq. (Hz)") +
  theme(legend.position="right") -> p2

fig1 %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=errors_pop*1e3, y=variances_pop*1e3, color=freq)) +
  geom_point(size=0.05, alpha=0.6) + 
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  scale_color_gradient(low="grey", high="black") +
  theme(legend.position="none") +
  labs(x="Error (ms)", y="Variance (ms)") -> p3

plot_grid <- rbind(c(1, 1, NA), c(2, 2, 2), c(3, 3, NA))
grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```

@@

```{r, fig.width=2.7, fig.height=2.3}
fig1 %>% 
  filter(rank == 0, freq == 20) %>% 
  ggplot(aes(x=As*1e9, y=V_osc*1e3)) +
  geom_point(size=0.1, alpha=0.6, color="black") + 
  labs(x="A (namp)", y="V_osc (mvolt)") +
  theme_classic() -> p1

fig1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=fig2, 
            aes(x=V_osc/V_comp, y=errors*1e3), 
            color="black", size=0.5) +
  labs(x="V_osc/V_comp", y="Error (ms)") -> p2

fig1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc/V_comp, y=variances*1e3)) +
  geom_point(size=0.01, alpha=0.01, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  theme_classic() +
  geom_line(data=fig2, 
            aes(x=V_osc/V_comp, y=variances*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x="V_osc/V_comp", y="Variance (ms)") -> p3

max_N <- max(fig1$N)

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 16, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors*1e3)) +
  geom_point(size=.1, alpha=0.1, color="grey") + 
  geom_vline(xintercept = 1, alpha=0.7, color="purple", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="purple", linetype="dashed") +
  facet_wrap(~rank, nrow=2) +
  theme_classic() + 
  scale_x_continuous(breaks=c(0, 1, 2)) +
  scale_y_continuous(breaks=c(0, 10)) +
  theme(
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) +
  labs(x="V_osc/V_comp", y="Error (ms)") -> p4

# plot_grid <- rbind(
#   c(1, 1, 2, 2, 2, 4, 4, 4), 
#   c(3, 3, 2, 2, 2, 4, 4, 4))
plot_grid <- rbind(
  c(1, 1, 2, 2, 2), 
  c(1, 1, 2, 2, 2), 
  c(3, 3, 2, 2, 2),
  c(3, 3, 2, 2, 2),
  c(4, 4, 4, 4, 4),
  c(4, 4, 4, 4, 4))
grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
rm(p1, p2, p3, p4, plot_grid, max_N)
```

# Bound 2 - n_spikes < (0, 1)

```{r}
max_N <- max(fig1$N)

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=errors, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=0.9) + 
  geom_vline(xintercept = 1, alpha=0.8) +
  geom_vline(xintercept = 0.5, alpha=0.4) +
  facet_wrap(~rank) +
  theme_classic() + 
  theme(
    legend.position="bottom", 
    strip.text.x = element_text(size=0),
    strip.background = element_blank()) +
  scale_colour_brewer(palette = "Accent") +
  xlab("V_osc/V_comp") 
```
